\documentclass[conference]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{url}
\usepackage{tagging}
\usepackage{fancyvrb}
\fvset{
  fontsize=\footnotesize,
  frame=leftline,
  framerule=0.7pt,
  rulecolor=\color{gray!60},
  framesep=4pt,
  xleftmargin=10pt,
  baselinestretch=1.05,
}

\usepackage{sc26repro}

%\usetag{explanation}
%\usetag{example}

\begin{document}

\twocolumn[%
{\begin{center}
\Huge
Appendix: Artifact Description
\end{center}}
]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  AD Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendixAD

\section{Overview of Contributions and Artifacts}

\subsection{Paper's Main Contributions}

\begin{description}
\item[$C_1$] \textbf{Bid-based reclamation interface.}
  A structured per-request bid abstraction that surfaces recoverable capacity
  and estimated disruption cost to the runtime scheduler, replacing implicit
  victim-ordering rules with an explicit decision interface.

\item[$C_2$] \textbf{Decoupled scoring-to-selection architecture.}
  Separation of request-level disruption estimation from coordinated
  cross-request victim selection through a uniform cost--capacity bid
  interface, so that the selection algorithm is independent of how
  disruption estimates are produced.

\item[$C_3$] \textbf{Portable runtime integration.}
  A non-invasive scheduling layer with a \texttt{FrameworkAdapter} abstraction
  demonstrated on vLLM~0.17.1 and SGLang, reusing each framework's native
  reclamation and recovery mechanisms without source-code modification.

\item[$C_4$] \textbf{Structured evaluation under controlled conditions.}
  Evaluation of five strategies varying across four scheduling dimensions
  (admission ordering, running-queue reordering, victim selection, proactive
  reclamation) under frozen request traces and calibrated arrival rates,
  enabling structured attribution across these co-varying dimensions.
\end{description}


\subsection{Computational Artifacts}

\begin{description}
\item[$A_1$] BidKV source code and experiment framework:\\
  \url{https://github.com/cybber695/bidkv}
\end{description}

\begin{center}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}rll@{}}
\toprule
Artifact ID & Contributions & Related Paper Elements \\
            & Supported     & \\
\midrule
$A_1$  & $C_1, C_2, C_3, C_4$ & Table~I (strategy differentiation) \\
       &                      & Table~II (rate sensitivity, vLLM) \\
       &                      & Table~III (long-context results) \\
       &                      & Table~IV (SGLang portability) \\
       &                      & Table~V (hyperparameter sensitivity) \\
       &                      & Figure~1 (motivation) \\
       &                      & Figure~2 (system architecture) \\
       &                      & Algorithm~1 (greedy victim ordering) \\
       &                      & Figure~3 (reclamation analysis) \\
       &                      & Figure~4 (victim-selection tradeoff) \\
\bottomrule
\end{tabular}%
}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Artifact Identification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newartifact

\artrel

$A_1$ comprises (i)~the BidKV Python package
(\texttt{src/bidkv/}), (ii)~vLLM and SGLang adapter layers
(\texttt{src/bidkv/adapters/}), (iii)~five strategy
implementations (\texttt{src/bidkv/baselines/}): PE, PE-SJF,
Static-Random, Largest-First, and BidKV, all invoked by~$T_2$,
and (iv)~the experiment runner, trace-freeze utilities, and analysis
scripts (\texttt{src/bidkv/experiments/}).
Together these components instantiate $C_1$--$C_3$ and drive all
measurements described in $C_4$.
The component--contribution mapping is:
\texttt{protocol/} and \texttt{solver/} implement the bid abstraction
and greedy utility-ranked selection ($C_1$, $C_2$);
\texttt{scoring/} and \texttt{baselines/} implement the decoupled
scoring-to-selection pipeline ($C_2$);
\texttt{adapters/} provides the \texttt{FrameworkAdapter} integration
for vLLM and SGLang ($C_3$);
\texttt{experiments/} provides frozen-trace replay, workload drivers,
and analysis scripts ($C_4$).

\artexp

Among all five vLLM strategies at rate~3.8\,req/s (mixed workload), BidKV
should achieve top-2 P95 TTFT (best-on-average $\approx$631\,ms) and
near-best 300\,ms SLO attainment ($\approx$83.2\,\%, second only to
Static-Random at $\approx$84.1\,\%) (Table~II).
Due to run-to-run variation in a live serving system, minor reorderings
among the top two strategies are expected; the reproducible claim is that
BidKV and Static-Random are consistently separated from the remaining
strategies on both P95 TTFT and SLO attainment.
Across all three arrival rates (2.0, 3.8, and 5.7\,req/s), BidKV should
rank first or second on both P95 TTFT and SLO attainment (Table~II).
On the long-context workload at peak load (rate~0.70\,req/s), BidKV should
achieve among the lowest P95 TTFT across all five strategies
(averaging $\approx$30{,}143\,ms; Table~III).
For the SGLang portability slice (Table~IV, rate~3.8\,req/s, mixed workload,
mean of 3~runs), BidKV should achieve 300\,ms SLO attainment of 93.2\,\%
and P95 TTFT of 337\,ms, versus 92.3\,\% and 386\,ms for Random-Evict,
and 54.4\,\% and 6{,}207\,ms for vanilla SGLang.
These results confirm that BidKV's admission-responsiveness gains are
directionally consistent across both vLLM and SGLang execution
environments.
For Table~V (hyperparameter sensitivity), BidKV's 300\,ms SLO attainment
and P95 TTFT should remain within approximately 2\,pp and 10\,\% of the
default configuration ($c_w{=}0.5$, $s_w{=}0.3$, gate\,=\,0.95) across the
full hyperparameter sweep ($c_w \in [0.25, 2.0]$, $s_w \in [0.1, 1.0]$,
KV-gate threshold $\in [0.85, 0.98]$), confirming that utility-ranked
selection is robust to disruption-weight choices.
These results substantiate $C_1$--$C_4$: the bid interface and
utility-ranked selection produce measurably better admission responsiveness
across two arrival-rate regimes and two workload types.

\arttime

\begin{itemize}
  \item \textbf{Artifact Setup:} 20--30\,min
    (conda environment creation, package installation, model download if not
    cached, trace generation).
  \item \textbf{Artifact Execution:}
    vLLM full matrix (5 strategies $\times$ 2 workloads $\times$ 3 rates
    $\times$ 3 runs = 90 experiment runs): $\approx$ 20--28\,h
    (mixed-workload runs average 5--8\,min each; long-context runs average
    20--25\,min each; server startup adds $\approx$4\,min per run).
    SGLang portability slice (3 strategies $\times$ rate~3.8\,req/s $\times$ 3~runs = 9~runs): $\approx$3--4\,h
    (each run averages 20--25\,min; server startup adds $\approx$4\,min per run).
    \textit{First-time SGLang execution requires an additional
    $\approx$30--60\,min for flashinfer JIT kernel compilation;
    subsequent runs use the \texttt{/root/.cache/flashinfer/} cache.}
    Hyperparameter sensitivity sweep ($T_5$, 10 variants $\times$ 3 runs):
    $\approx$4--5\,h (independent of $T_2$/$T_3$; can be run on the same GPU
    before or after $T_2$/$T_3$ on a single-GPU machine).
  \item \textbf{Artifact Analysis:} 5--10\,min
    (single analysis script invocation per result directory).
\end{itemize}

\artin

\artinpart{Hardware}

\begin{itemize}
  \item Single NVIDIA GPU, Compute Capability $\geq$\,8.0 (Ampere or
    newer); RTX~A6000 48\,GiB used in this evaluation.
    CUDA~12.8 driver with nvcc~12.8 required for SGLang kernel
    compilation (\texttt{cuda-nvcc-12-8} from the NVIDIA apt repository);
    single-node, single-GPU only---distributed execution is not supported.
  \item $\geq$64\,GiB system RAM; $\geq$8 CPU cores recommended.
  \item $\geq$40\,GB free disk space (model weights, result files).
\end{itemize}

\artinpart{Software}

\begin{itemize}
  \item Python~3.10 or 3.11
  \item conda (Miniconda/Anaconda) for environment management
  \item vLLM~0.17.1 (\url{https://github.com/vllm-project/vllm})
  \item SGLang~0.5.9 (\url{https://github.com/sgl-project/sglang})
    with flashinfer~0.6.3 (attention kernel backend).
    \textit{Note:} SGLang requires CUDA~12.0+ nvcc for JIT kernel
    compilation (flashinfer and TVM rope kernel). The system
    \texttt{apt} package \texttt{nvidia-cuda-toolkit} ships nvcc~11.5
    and is \emph{not} sufficient; install \texttt{cuda-nvcc-12-8} from
    the NVIDIA official apt repository instead
    (\texttt{/usr/local/cuda-12.8/bin/nvcc}).
    SGLang and vLLM share one conda environment in this artifact.
  \item BidKV package (this artifact; zero external dependencies beyond
    vLLM/SGLang, which are runtime-only imports in the adapter layer)
\end{itemize}

\artinpart{Datasets / Inputs}

The experiment uses the ShareGPT Vicuna unfiltered dataset
(\url{https://huggingface.co/datasets/anon8231489123/ShareGPT_Vicuna_unfiltered}).
Request traces are deterministically generated from this dataset using
seed~42 and frozen by SHA-256 checksums.
The trace-freeze script is included in the artifact:

\begin{Verbatim}
FREEZE=bidkv.experiments.vllm.freeze_traces
python -m $FREEZE \
    --mode formal --use-frozen-rates \
    --output-dir experiments/vllm/traces/
\end{Verbatim}


The model weights are Llama-3.1-8B-Instruct
(\url{https://huggingface.co/meta-llama/Llama-3.1-8B-Instruct}).
Access requires a HuggingFace account with an approved model-access
request; submit the form on the model page (approval is typically
granted within minutes).
If a local HuggingFace cache is available, set
\texttt{HF\_HUB\_OFFLINE=1} and \texttt{TRANSFORMERS\_OFFLINE=1}.

\artinpart{Installation and Deployment}

\begin{Verbatim}
# 1. Create conda environment
conda create -n bidkv python=3.10 -y
conda activate bidkv

# 2. Install vLLM and SGLang
pip install vllm==0.17.1
# SGLang 0.5.9 with flashinfer 0.6.3:
pip install "sglang[all]==0.5.9"

# 3. SGLang requires CUDA 12+ nvcc.
#    apt nvidia-cuda-toolkit: nvcc 11.5 (old).
#    Use the NVIDIA official apt repository:
apt-get install -y cuda-nvcc-12-8
# clears stale JIT cache if present:
rm -rf /root/.cache/flashinfer

# 4. Install BidKV (editable)
cd /path/to/bidkv && pip install -e ".[dev]"

# 5. Generate frozen traces (shared by all)
FREEZE=bidkv.experiments.vllm.freeze_traces
python -m $FREEZE \
    --mode formal --use-frozen-rates \
    --output-dir experiments/vllm/traces/
\end{Verbatim}


BidKV itself has no compiled components; all C/CUDA compilation
is performed by SGLang's flashinfer JIT on first server startup
($\approx$5--15\,min, then cached in \texttt{/root/.cache/flashinfer/}).
Set the following environment variables before running SGLang experiments:
\begin{Verbatim}
export CUDA_HOME=/usr/local/cuda-12.8
export PATH="/usr/local/cuda-12.8/bin:$PATH"
export HF_HUB_OFFLINE=1
export TRANSFORMERS_OFFLINE=1
# Prevent proxy blocking health checks:
export no_proxy="127.0.0.1,localhost"
export NO_PROXY="127.0.0.1,localhost"
\end{Verbatim}


\artcomp

\textbf{Workflow tasks and dependencies:}

\begin{itemize}
  \item $T_1$ \textbf{Trace generation.}
    \texttt{freeze\_traces.py} samples 1\,000 requests (mixed) and 500
    requests (long-context) from ShareGPT with seed~42 and writes
    SHA-256-verified JSON trace files to \texttt{experiments/vllm/traces/}.

  \item $T_2$ \textbf{vLLM experiment execution.}
    \texttt{runner.py} iterates over 5 strategies $\times$ 2 workloads
    $\times$ 3 arrival rates $\times$ 3 runs.
    For each strategy it starts a vLLM server (BidKV scheduler hooks are
    injected via the \texttt{vllm.general\_plugins} entry point for all
    strategies; preempt-evict installs a no-op FCFS hook identical to
    vanilla vLLM for measurement fairness), replays the frozen trace using a
    Poisson open-loop arrival model, collects per-request TTFT and
    completion-token counts, and writes one JSON result file per run.
    Fixed server parameters: \texttt{--gpu-memory-utilization~0.5},
    \texttt{--num-gpu-blocks-override~600}, \texttt{--max-num-seqs~32},
    \texttt{--block-size~16}, \texttt{--max-model-len~8192},
    \texttt{--enforce-eager}, \texttt{--disable-frontend-multiprocessing},
    \texttt{--no-enable-prefix-caching}.
    The runner supports \texttt{--resume} to skip already-completed
    runs; on failure (OOM or server crash), delete the partial result
    file and re-invoke with \texttt{--resume} to continue.
    Invocation:
    \begin{Verbatim}
STRATS="preempt-evict,preempt-evict-sjf,"
STRATS+="static-random,largest-first,bidkv"
python -m bidkv.experiments.vllm.runner \
    --strategies "$STRATS" \
    --workloads mixed,long_context \
    --mixed-rates 2.0,3.8,5.7 \
    --long-rates 0.35,0.5,0.7 \
    --runs 3 \
    --gpu-memory-utilization 0.5 \
    --num-gpu-blocks-override 600 \
    --max-model-len 8192 \
    --output-dir results/vllm_full/ \
    --traces-dir experiments/vllm/traces/ \
    --resume
    \end{Verbatim}

  \item $T_3$ \textbf{SGLang portability execution.}
    Uses the SGLang runner (\texttt{experiments/sglang/runner.py}) with
    3 strategies (BidKV, Random-Evict, vanilla SGLang) $\times$
    rate~3.8\,req/s $\times$ 3 runs.
    Strategy name mapping: code name \texttt{sglang\_default} corresponds
    to paper name ``vanilla SGLang''; \texttt{static-random} corresponds
    to ``Random-Evict''.
    Fixed server parameters: \texttt{--mem-fraction-static~0.85},
    \texttt{--max-total-tokens~9600}, \texttt{--attention-backend~triton}
    (triton backend is required to avoid a \texttt{flashinfer}/\texttt{sgl\_kernel}
    incompatibility with PyTorch~2.6; flashinfer is still installed for
    SGLang's other kernels).
    The runner is invoked as:
    \begin{Verbatim}
STRATS=sglang_default,static-random,bidkv
python -m bidkv.experiments.sglang.runner \
    --strategies "$STRATS" \
    --workloads "mixed" --mixed-rates "3.8" \
    --runs 3 --max-total-tokens 9600 \
    --attention-backend triton \
    --output-dir results/sglang_portability/ \
    --traces-dir experiments/vllm/traces/ \
    --resume
\end{Verbatim}

    Results are included in Table~IV.

  \item $T_4$ \textbf{Analysis.}
    \texttt{analysis.py} reads all JSON result files, computes P95 TTFT,
    TPOT P95, throughput, and SLO attainment (from raw per-request data;
    P95 and SLO are not pre-computed), and produces tables and figures.
    Invocation (run once per result directory):
    \begin{Verbatim}
# vLLM results
python -m bidkv.experiments.vllm.analysis \
    --results-dir results/vllm_full/ \
    --output-dir results/vllm_full/analysis/
# SGLang results
RDIR=results/sglang_portability
python -m bidkv.experiments.sglang.analysis \
    --results-dir "$RDIR/" \
    --output-dir "$RDIR/analysis/"
    \end{Verbatim}

  \item $T_5$ \textbf{Hyperparameter sensitivity (Table~V).}
    Run 10 parameter variants ($\times$ 3 runs each,
    $\approx$4--5\,h on a single GPU):
    \begin{Verbatim}
mkdir -p results/vllm_sensitivity_v2
nohup bash scripts/run_sensitivity_v2.sh \
    > results/vllm_sensitivity_v2/run.log \
    2>&1 &
    \end{Verbatim}
    Then verify the robustness conclusions:
    \begin{Verbatim}
python scripts/analyze_sensitivity_v2.py
    \end{Verbatim}

\end{itemize}

\textbf{Dependencies:} $T_1 \rightarrow T_2 \rightarrow T_4$;
$T_1 \rightarrow T_3 \rightarrow T_4$.
$T_2$ and $T_3$ are independent; on a single-GPU machine they must be
run sequentially ($T_2$ first, then $T_3$).
Parallel execution requires two GPUs.
$T_5$ is independent of $T_1$--$T_4$.

\textbf{Experimental parameters:}
\begin{itemize}
  \item Mixed workload: 1\,000 requests, rates $\{2.0, 3.8, 5.7\}$\,req/s,
    3 runs per (strategy, rate) combination.
  \item Long-context workload: 500 requests,
    rates $\{0.35, 0.5, 0.7\}$\,req/s, 3 runs per combination.
  \item SGLang portability ($T_3$): mixed workload,
    rate~3.8\,req/s, 3 runs per strategy.
  \item KV capacity fixed at 600 blocks (9\,600 tokens) to induce
    sustained KV pressure; \textbf{this parameter must not be changed.}
    Reducing it below this threshold eliminates KV pressure, causing all
    strategies to converge to near-identical behavior and making strategy
    differentiation impossible to observe.
  \item Arrival process: Poisson (open-loop); seed~42 for trace replay.
\end{itemize}

\artout

Raw results are stored as JSON files with naming convention
\texttt{strategy\_\_workload\_\_rate\{r\}\_\_r\{i\}.json}
in the designated result directory.
Each file contains per-request TTFT, total latency, completion-token count,
and adapter-level reclamation metrics.

Analysis scripts in \texttt{experiments/vllm/} and
\texttt{experiments/sglang/} read these files and compute P95/P50
TTFT, TPOT P95, throughput, and SLO attainment from raw
per-request data (P95 and SLO are not pre-computed in the JSON).
Outputs are JSON metric files (supporting Tables~II--IV) and a PDF
reclamation figure (Figure~3). Table~V (hyperparameter sensitivity)
is produced by $T_5$ (\texttt{scripts/run\_sensitivity\_v2.sh} +
\texttt{scripts/analyze\_sensitivity\_v2.py}), not by
\texttt{experiments/vllm/analysis.py}.
Figures~1--2, Algorithm~1, and Figure~4 are pre-generated static
assets in \texttt{paper/figures/} and are not produced by the
analysis scripts.
The scripts handle the legacy field-name difference between older
result batches (\texttt{total\_compressions}) and newer ones
(\texttt{total\_evictions}).

\end{document}
